---
title: "p8105_hw1_xx2554"
output: github_document
date: "2026-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

## Problem 1
```{r}
library(tidyverse)

data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains information about penguins, including species, island, bill length, bill depth, flipper length, body mass, sex, and year. The `species` variable includes Adelie, Chinstrap, and Gentoo penguins, and the `island` variable includes Biscoe, Dream, and Torgersen. The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

```{r}
ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point()

ggsave("penguins_scatterplot.png")
```


## Problem 2
```{r}
problem2_df = tibble(
  random_sample = rnorm(10),
  positive = random_sample > 0,
  character_vec = c(
    "latte", "americano", "cappuccino", "mocha", "espresso",
    "macchiato", "flat white", "cold brew", "cortado", "affogato"
  ),
  factor_vec = factor(
    c(
      "small", "medium", "large", "small", "medium",
      "large", "small", "medium", "large", "small"
    )
  )
)

problem2_df
```

```{r}
mean(pull(problem2_df, random_sample))
mean(pull(problem2_df, positive))
mean(pull(problem2_df, character_vec))
mean(pull(problem2_df, factor_vec))
```
The mean works for the numeric and logical variables, but not for the character or factor variables. The mean of `random_sample` is `r mean(pull(problem2_df, random_sample))`. For the logical variable, R treats `TRUE` as 1 and `FALSE` as 0, so its mean is `r mean(pull(problem2_df, positive))`, which means that `r mean(pull(problem2_df, positive)) * 100`% of the values are `TRUE`. The character and factor variables do not have directly meaningful numeric means.
